Visualizing predictions

### 2021-02-21 effects_writeup.Rnw
Autocommit

First, we include the intercept variance in the variable effects:

@@

\begin{figure}[H]
\begin{center}
<<contr_model_predictions_plot, fig=TRUE, echo=FALSE>>=
contr_pred_all_plot_out
@
\end{center}
\caption{Variable effects with intercept and other non-focal predictor uncertainties included. The legend compares the model with non contrast (\code{x2u}) to the one with sum to zero contrast (\code{x2c}).}
\label{fig:contr_pred_plot}
\end{figure}

@@

As explained in the previous section, we again eliminate the uncertainties due to the intercept term and the non-focal variables.

@@

\begin{figure}[H]
\begin{center}
<<contr_zeroed_vcov_plot, fig=TRUE, echo=FALSE>>=
contr_pred_zeroed_vcov_plot
@
\end{center}
\caption{Variable effects with intercept and other non-focal predictor uncertainties included. The legend compares the model with non contrast (\code{x2u}) to the one with sum to zero contrast (\code{x2c}).}
\label{fig:contr_zeroed_vcov}
\end{figure}

@@

@@

\begin{figure}[H]
\begin{center}
<<contr_zeroed_mmat_plot, fig=TRUE, echo=FALSE>>=
contr_pred_zeroed_mmat_plot
@
\end{center}
\caption{Variable effects with intercept and other non-focal predictor uncertainties included. The legend compares the model with non contrast (\code{x2u}) to the one with sum to zero contrast (\code{x2c}).}
\label{fig:contr_zeroed_mmat}
\end{figure}

>>>>

\autoref{fig:contr_pred_plot} compares variable effects for the three packages when the variance of the non-focal predictors are included.

@@

\begin{figure}[H]
\begin{center}
<<contr_model_predictions_plot, fig=TRUE, echo=FALSE>>=
contr_pred_all_plot_out
@
\end{center}
\caption{Variable effects with non-focal predictors' uncertainties included. The legend compares the model with non contrast (\code{x2u}) to the one with sum to zero contrast (\code{x2c}).}
\label{fig:contr_pred_plot}
\end{figure}

@@

As explained in the previous section, we again eliminate the uncertainties due to non-focal predictors.

@@

\begin{figure}[H]
\begin{center}
<<contr_zeroed_vcov_plot, fig=TRUE, echo=FALSE>>=
contr_pred_zeroed_vcov_plot
@
\end{center}
\caption{Here, we eliminate uncertainties using zeroed-variance covariance approach. All the three methods give similar estimates for the model with non contrast (\code{x2u}) to the one with sum to zero contrast (\code{x2c}), respectively. In comparing, \code{x2u} with \code{x2c}, the uncertainties around the baseline category is completely eliminated.}
\label{fig:contr_zeroed_vcov}
\end{figure}

@@

Currently, only \pkg{varpred} provides a way to center the model matrix.

@@

\begin{figure}[H]
\begin{center}
<<contr_zeroed_mmat_plot, fig=TRUE, echo=FALSE>>=
contr_pred_zeroed_mmat_plot
@
\end{center}
\caption{We set \code{isolate = TRUE} in \pkg{varpred} to use centered model matrix in computing the CIs. In this case, predictions for both non contrasted (\code{x2u}) and contrasted (\code{x2c}) models are the same in \pkg{varpred}. Also, the CIs are slightly different with those in \autoref{fig:contr_zeroed_vcov}. \JD{Steve -> JD: Weighted contrast?}.}
\label{fig:contr_zeroed_mmat}
\end{figure}
